---
title: "CSCI E-63C: Week 1 Problem Set"
author: "Christopher Eshleman" 
output:
  html_document:
    toc: true
---

```{r setup, include=FALSE}
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list=ls()) # clear the global environment 
```

# Problem 1 (30 points).

###Reproduce example from class: 

```{r}
m <- matrix(0) 
n <- numeric(1000) 
for ( i in 1:1000 ) {
     m[i] <- mean(rnorm(20))
}
#m[1:8]
hist(m, col="pink") 
#sum(abs(m)>0.3) 
```

###Practice practice practice: 

```{r}
rm(list=ls()) # clear the global environment 

# Now build upward from the ground level. 

head(rnorm(1000)) # This gives us our 1000 sample. 
mean(rnorm(1000)) # Here is hte mean of that 1000-number sample.
bb <- numeric(0) # A recepticle for results (the means of each 1000-number sample).
for(aa in 1:3) { # Generate means (three) for the recepticle. This is a vector. 
  bb[aa] <- mean(rnorm(1000)) 
}
sd(bb) # Find the standard deviation of that vector. 
sizes <- c(3,5) # Here are two sample sizes instead of one. 
sds <- numeric(0) # A recepticle for the standard deviations of the means. 

#for ( N in 1:sizes ) { # try different sample sizes 
#  for(aa in 1:3) {
#  bb[aa] <- mean(rnorm(1000)) 
#  }
#  sds[N] <- sd(bb)
#} 
```

###Main main main: 

```{r sem,eval=FALSE}

rm(list=ls()) # clear the global environment 

sample.sizes=c(3,10,50,100,500,1000) 
m <- numeric(0) 
mean.sds <- numeric(0) 

for ( N in sample.sizes ) { # try different sample sizes 
  
} 

plot(sample.sizes,mean.sds, main="SEM vs sample size",pch=19)
lines(sample.sizes,1/sqrt(sample.sizes),col='blue')
```


# Problem 2 (30 points).

###Main main main: 


```{r,eval=TRUE}
N1 <- 1 

n.repeats <- 1000 
s.values1 <- numeric() 
for (i.exp in 1:n.repeats) { 
   x1 <- runif(N1) 

  s.values1[i.exp] <- sum(x1) 
}
```

```{r,eval=TRUE}
N2 <- 500  

n.repeats <- 1000 
s.values2 <- numeric() 

for (i.exp in 1:n.repeats) { 

   x2 <- runif(N2)  #rnorm(N) 

  s.values2[i.exp] <- sum(x2) 
}
```

```{r,eval=TRUE} 
#{r clt,eval=TRUE}
N3 <- 20  # the number of i.i.d. variables X we are going to sum

n.repeats <- 1000 
s.values3 <- numeric() 
for (i.exp in 1:n.repeats) { # repeat the experiment 'n.repeats' times

   x3 <- runif(N3) 

  s.values3[i.exp] <- sum(x3) 
}
```


```{r}
init <- par(no.readonly=TRUE)
par(mfrow=c(1,3))

hist(s.values1,breaks=20,col='lightgreen', main = paste("N=",N1))
hist(s.values2,breaks=20,col='lightgreen', main = paste("N=",N2))
hist(s.values3,breaks=20,col='lightgreen', main = paste("N=",N3))
```


```{r}
par(init)
```


###Response to final question (5 points): 

The sample will be normally distributed with an expected mean equal to the *population mean*, as it is a sample of the underlying population, if we assume sampling was random in nature. The sample's distribution as N increases moves closer and closer toward a normal distribution, centered on 0 (zero) with a standard deviation of 1 (one). 


